---
title: "Pollution to human transmission of COVID-19 in Catalonia"
author: "Authors"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{covid19dataexplorations}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(covid19dataexplorations)
```




**THIS IS WORK IN PROGRESS**


Exploration to replicate an italian paper on pollution to human transmission of COVID-19

## Original paper

Diffusion of COVID-19 Outbreaks: The Interaction between Air Pollution-to-Human and Human-to-Human Transmission Dynamics in Hinterland Regions with Cold Weather and Low Average Wind Speed
https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3567841

## Required datasets

| Dataset | Description | Source |
|---------|--------|------|
| covid_tests_catalonia | Number of infected per city | Tests of COVID-19 in Catalonia, Government of Catalonia | 
| | Meteorological indicators: average, moisture, wind, days of rain and fog | |
| | density | |
