---
title: "Pollution to human transmission of COVID-19 in Catalonia"
author: "Authors"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{covid19dataexplorations}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(covid19dataexplorations)
```




**THIS IS WORK IN PROGRESS**

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

Exploration to replicate an italian paper on pollution to human transmission of COVID-19

## Original paper

Diffusion of COVID-19 Outbreaks: The Interaction between Air Pollution-to-Human and Human-to-Human Transmission Dynamics in Hinterland Regions with Cold Weather and Low Average Wind Speed
https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3567841

## Required datasets

| Dataset | Description | Source |
|---------|--------|------|
| covid_tests_catalonia | Number of infected per city | Tests of COVID-19 in Catalonia, Government of Catalonia | 
| | Meteorological indicators: average, moisture, wind, days of rain and fog | |
| | density | |


## Analysis

```{r munge}
library(tidyverse)
library(stargazer)
library(ggeffects)

load("../data/covid_tests_catalonia.rda")

covid_tests_catalonia <- covid_tests_catalonia %>% 
  mutate(RegioSanitariaDescripcio = as_factor(RegioSanitariaDescripcio)) %>% 
  mutate(RegioSanitariaDescripcio = relevel(RegioSanitariaDescripcio, ref="Barcelona"))
```


```{r mod1, results='asis'}
mod1 <- lm(ResultatCovidCodi~SexeDescripcio, data=covid_tests_catalonia)
mod2 <- update(mod1,.~. + RegioSanitariaDescripcio)

stargazer(mod1,mod2,
          type="html",
          no.space = TRUE,
          header=FALSE)

```

```{r sex, fig.width=6}
p <- ggpredict(mod2,terms = "SexeDescripcio") %>% as_tibble()

ggplot(p, aes(x,predicted)) +
  geom_point() +
  geom_errorbar(aes(ymin=conf.low, ymax=conf.high),
                width=0.05) +
  theme_minimal() +
  labs(x="",
       y="Probabilitat de positiu de COVID19") +
  ylim(0.41,0.49)
```



```{r regio, fig.width=6}
p <- ggpredict(mod2,terms = "RegioSanitariaDescripcio") %>% as_tibble()

ggplot(p, aes(predicted,reorder(x,desc(predicted)))) +
  geom_point() +
  geom_errorbarh(aes(xmin=conf.low, xmax=conf.high),
                height=0.05) +
  theme_minimal() +
  labs(y="",
       x="Probabilitat de positiu de COVID19") +
  theme(axis.text.y = element_text(hjust=0))

```

